\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-03-24 papers/jss/article.Rnw
Better fix.  Add a new proto with only the examples we need for this paper rather than pulling in all fo the complexity of TestAllTypes or faking it with CodeInput/CodeOutput.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@881 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<<echo=FALSE,print=FALSE>>=
if (!exists("protobuf_unittest.TestAllTypes",
            "RProtoBuf:DescriptorPool")) {
    unittest.proto.file <- system.file("unitTests", "data",
                                       "unittest.proto",
                                       package="RProtoBuf")
    readProtoFiles(file=unittest.proto.file)
}
@

% We want a cleaner error message here.
\begin{CodeChunk}
\begin{CodeInput}
R> a <- new(protobuf_unittest.TestAllTypes)
R> a$optional_bool <- TRUE
R> a$optional_bool <- FALSE
R> a$optional_bool <- NA
\end{CodeInput}
\begin{CodeOutput}
Error: NA boolean values can not be stored in bool Protocol Buffer fields
\end{CodeOutput}
\end{CodeChunk}

@@

<<>>=
test <- new(protobuf_unittest.TestAllTypes)
test$repeated_int64 <- c(2^53, 2^53+1)
length(unique(test$repeated_int64))
@

>>>>

<<echo=FALSE,print=FALSE>>=
if (!exists("JSSPaper.Example1", "RProtoBuf:DescriptorPool")) {
    readProtoFiles(file="int64.proto")
}
@

% We want a cleaner error message here.
\begin{CodeChunk}
\begin{CodeInput}
R> a <- new(JSSPaper.Example1)
R> a$optional_bool <- TRUE
R> a$optional_bool <- FALSE
R> a$optional_bool <- NA
\end{CodeInput}
\begin{CodeOutput}
Error: NA boolean values can not be stored in bool Protocol Buffer fields
\end{CodeOutput}
\end{CodeChunk}

@@

<<>>=
test <- new(JSSPaper.Example1)
test$repeated_int64 <- c(2^53, 2^53+1)
length(unique(test$repeated_int64))
@
